---
title: 'Video 7: lasso with the Office'
author: "Josh Erickson"
date: "7/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Highlights: str_trim() takes away spaces at beginning and end of string!
separate_rows() is really useful for separating rows by some pattern.
workflows() are really handy and I can see myself using them more in the future.

```{r}
library(tidyverse)

theme_set(theme_bw())
```

Let's train a LASSO using tidymodels for [The Office episode ratings from #tidytuesday data](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-03-17/readme.md)

```{r}
tuesdata <- tidytuesdayR::tt_load('2020-03-17')

ratings_raw <- tuesdata$office_ratings

#clean up the string title
remove_regex <- "[:punct:]|[:digit:]|parts |part |the |and"

office_ratings <- ratings_raw %>% 
  transmute(episode_name = str_to_lower(title),
            episode_name = str_remove_all(episode_name, remove_regex),
            episode_name = str_trim(episode_name),
            imdb_rating)
office_info <- schrute::theoffice %>% 
  mutate(season = as.numeric(season),
         episode = as.numeric(episode),
         episode_name = str_to_lower(episode_name),
            episode_name = str_remove_all(episode_name, remove_regex),
            episode_name = str_trim(episode_name)) %>% 
  select(season, episode, episode_name, director, writer, character)
```
## Explore Data

Now explore
```{r}
library(skimr)

skim(office_ratings)

characters <- office_info %>% 
  count(episode_name, character) %>% 
  add_count(character, wt=n, name = 'character_count') %>% 
  filter(character_count > 0) %>% 
  select(-character_count) %>% 
  pivot_wider(names_from = character,
              values_from = n,
              values_fill = list(n=0))

creators <- office_info %>% 
  distinct(episode_name, director, writer) %>% 
  pivot_longer(c('director', 'writer'), names_to = 'role', values_to = 'person') %>% 
  separate_rows(person, sep = ';') %>% 
  add_count(person) %>% 
  filter(n > 10) %>% 
  distinct(episode_name, person) %>% 
  mutate(person_value = 1) %>% 
  pivot_wider(names_from = person, 
              values_from = person_value,
              values_fill = list(person_value = 0))

office <- office_info %>% 
  distinct(season, episode, episode_name) %>% 
  inner_join(characters) %>% 
  inner_join(creators) %>% 
  inner_join(office_ratings) %>% 
  janitor::clean_names()
```

```{r}
office %>% 
  ggplot(aes(episode, imdb_rating, fill = as.factor(episode))) + 
  geom_boxplot(show.legend = F)
```

## Now start modeling!

```{r}
library(tidymodels)

office_split <- initial_split(office, strata = season)

office_train <- training(office_split)
office_test <- testing(office_split)


```

Let's recipe!
```{r}
office_rec <- recipe(imdb_rating ~ ., data = office_train) %>% 
  update_role(episode_name, new_role = 'bring_along') %>% 
  step_zv(all_numeric(), -all_outcomes()) %>% 
  step_normalize(all_numeric(), -all_outcomes()) 

office_prep <- office_rec %>% 
  prep(strings_as_factors = FALSE)
```


```{r}
lasso_spec <- linear_reg(penalty = 0.1, mixture = 1) %>% 
  set_engine('glmnet')

wf <- workflow() %>% 
  add_recipe(office_rec)

lasso_fit <- wf %>% add_model(lasso_spec) %>% 
  fit(data = office_train)

lasso_fit %>% 
  pull_workflow_fit() %>% 
  tidy()
```

## Tune LASSO parameters

```{r}
set.seed(1234)
office_boot <- bootstraps(office_train, strata = season)

lambda_grid <- grid_regular(penalty(),
             levels = 50)

tune_spec <- linear_reg(penalty = tune(), mixture = 1) %>% 
  set_engine('glmnet')


set.seed(12342)
lasso_grid <- tune_grid(wf %>% add_model(tune_spec),
          resamples = office_boot,
          grid = lambda_grid)
```


```{r}
lasso_grid %>% 
  collect_metrics() %>% 
  ggplot(aes(penalty, mean, color = .metric)) +
  geom_line(show.legend = F) +
  facet_wrap(~.metric, scales = 'free', nrow = 2) +
  scale_x_log10()
```

```{r}
lowest_rmse <- lasso_grid %>% 
  select_best('rmse')

final_lasso <- finalize_workflow(wf %>% add_model(tune_spec),
                                 lowest_rmse)


library(vip)

final_lasso %>% 
  fit(office_train) %>% 
  pull_workflow_fit() %>% 
  vip::vi(lambda = lowest_rmse$penalty) %>% 
  mutate(Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance)) %>% 
  ggplot(aes(x = Importance, y = Variable, fill = Sign)) +
  geom_col() + 
  scale_x_continuous(expand = c(0,0)) + 
  labs(y = NULL)
```

























