---
title: 'Video 2: Modeling hotel bookings in R using tidymodels and recipes'
author: "Josh Erickson"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(thematic)
theme_set(theme_bw())
thematic::thematic_on(font = 'Roboto Mono')
```

# Predicting Hotel Bookings

## Pre-Processing/Explore Data

We'll build a model using tidytuesday data from [#tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-11/readme.md).


Bring in the data.

```{r}
hotels <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv')


hotel_stays <- hotels %>% filter(is_canceled == 0) %>% 
  mutate(children = case_when(children + babies > 0 ~ 'children',
                              TRUE ~ 'none'),
         required_car_parking_spaces = case_when(required_car_parking_spaces > 0 ~ 'parking',
                                                 TRUE ~ 'none')) %>% 
  select(-is_canceled, -reservation_status, -babies)

hotel_stays

hotel_stays %>% count(children)


```


Using skimmer to look explore the dataframe quickly. I normally use `glimpse()` but now i'm going to use this because it is freaking awesome!

```{r}
library(skimr)

skim(hotel_stays)
```

We'll look at some feature engineering with this type of data.

Explore some plots.

```{r}
hotel_stays %>% 
  mutate(arrival_date_month = factor(arrival_date_month, levels = month.name)) %>% 
  count(hotel, arrival_date_month, children) %>% 
  group_by(hotel, children) %>% 
  mutate(proportion = n/sum(n)) %>% 
  ggplot(aes(arrival_date_month, proportion, fill = children)) +
  geom_col(position = 'dodge') + facet_wrap(~hotel, nrow = 2)
```

```{r}
hotel_stays %>%  
  count(hotel, required_car_parking_spaces, children) %>% 
  group_by(hotel, children) %>% 
  mutate(proportion = n/sum(n)) %>% 
  ggplot(aes(required_car_parking_spaces, proportion, fill = children)) +
  geom_col(position = 'dodge') + facet_wrap(~hotel, nrow = 2)
```

Look at GGally

```{r}
library(GGally)

hotel_stays %>% sample_n(size = 1000) %>% 
  select(children, adr, required_car_parking_spaces, total_of_special_requests) %>% 
  ggpairs(mapping = aes(color = children))
```

Now let's build a model with recipes and tidymodels!

```{r}
hotels_df <- hotel_stays %>% 
  select(children, hotel, arrival_date_month, meal, adr, adults,required_car_parking_spaces, total_of_special_requests, stays_in_week_nights, stays_in_weekend_nights) %>% 
  mutate(across(where(is.character), factor))
skim(hotels_df)


```

Load up tidymodels.


```{r}
library(tidymodels)

set.seed(1234)

hotel_split <- initial_split(hotels_df)

hotel_train <- training(hotel_split)
hotel_test <- testing(hotel_split)


```

Now let's build a recipe! Good for pre-processing and feature engineering, like really good. Ultimately we don't want to leak data aka data leakage. This helps lessen that affect.

```{r}

hotel_rec <- recipe(children ~ ., data = hotel_train) %>% 
  themis::step_downsample(children) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_numeric()) %>% 
  step_normalize(all_numeric()) %>% 
  prep()

test_proc <- bake(hotel_rec, new_data = hotel_test)

```

Let's do a nearest neighbor model.

```{r}
install.packages('kknn')
knn_spec <- nearest_neighbor() %>% 
  set_engine('kknn') %>% 
  set_mode('classification')

knn_fit <- knn_spec %>% 
  fit(children ~ ., data = juice(hotel_rec))

knn_fit

```

Now a decision tree.

```{r}
tree_spec <- decision_tree() %>% 
  set_engine('rpart') %>% 
  set_mode('classification')

tree_fit <- tree_spec %>% 
  fit(children ~ ., 
      data = juice(hotel_rec))

tree_fit
```


## Evaluate models

Time to validate.

```{r}
set.seed(1234)

validation_splits <- mc_cv(juice(hotel_rec), prop = 0.9, strata = children)

knn_result <- fit_resamples(knn_spec,
                            children ~ ., 
              validation_splits,
             control = control_resamples(save_pred = T))


knn_result %>% collect_metrics()

tree_result <- fit_resamples(tree_spec,
                            children ~ ., 
              validation_splits,
              control = control_resamples(save_pred = T))


tree_result %>% collect_metrics()

```

Look at the results visually now.

```{r}
knn_result %>% 
  unnest(.predictions) %>% 
  mutate(model = 'kknn') %>% 
  bind_rows(tree_result %>% 
              unnest(.predictions) %>% 
              mutate(model = 'rpart')) %>% 
  group_by(model) %>% 
  roc_curve(children, .pred_children) %>% 
  autoplot()

knn_result %>% 
  unnest(.predictions) %>% 
  conf_mat(children, .pred_class) %>% 
  autoplot(type = 'heatmap')
```

```{r}
knn_fit %>% 
  predict(new_data = test_proc, type = 'prob') %>% 
  mutate(truth = hotel_test$children) %>% 
  roc_auc(truth, .pred_children) 

tree_fit %>% 
  predict(new_data = test_proc, type = 'prob') %>% 
  mutate(truth = hotel_test$children) %>% 
  roc_auc(truth, .pred_children) 


```























