---
title: 'Video 2: Predictive modeling in R with tidymodels and NFL attendance'
author: "Josh Erickson"
date: "4/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(silgelib)
library(scales)
library(lubridate)
theme_set(theme_plex())
```

## Explore data

We'll build a simple model using [NFL attendance from #tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-04/readme.md). 

Read in the data.

```{r}

attendance <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/attendance.csv')
standings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/standings.csv')

attendance_join <- attendance %>% left_join(standings, by = c('year', 'team_name', 'team'))

```

EDA with this data, it's important!

```{r}
attendance_join %>% mutate(team_name = fct_reorder(team_name, weekly_attendance, median, na.rm = T)) %>% 
  ggplot(aes(team_name, weekly_attendance, fill = playoffs)) + geom_boxplot(outlier.alpha = 0.5) + coord_flip() + scale_y_continuous(labels = comma) + facet_wrap(~year, scales = 'free')


attendance_join %>% mutate( year_week = paste0(year,'-', week),team_name = fct_reorder(team_name, -weekly_attendance, median, na.rm = T)) %>% 
  ggplot(aes(year_week, weekly_attendance, color = team_name, group = team_name)) +
  geom_line(show.legend = F) + geom_smooth(method = 'lm', se = FALSE,show.legend = F) + scale_y_continuous(labels = comma) +
  facet_wrap(~team_name)


```

Looking at margin of victory and playoff occurrence?

```{r}
attendance_join %>% distinct(team_name, year, margin_of_victory, playoffs) %>%  ggplot(aes(margin_of_victory, fill = playoffs)) + geom_histogram(position = 'identity', alpha = 0.7)
```
 

```{r}
attendance_join %>% 
  mutate(week = factor(week)) %>% 
  ggplot(aes(week, weekly_attendance, fill = week)) + 
  geom_boxplot(show.legend = F) + facet_wrap(~playoffs)
```

Now let's build the dataset!

```{r}
attendance_df <- attendance_join %>% 
  filter(!is.na(weekly_attendance)) %>% 
  select(weekly_attendance, team_name, year, week,
         margin_of_victory, strength_of_schedule, playoffs)
```

## Train model

Load tidymodels!

```{r}
library(tidymodels)

attendance_split <- attendance_df %>% 
  initial_split(strata = playoffs)


nfl_train <- training(attendance_split)
nfl_test <- testing(attendance_split)
```

Now let's build some models. Linear regression and random forest. More than the normal `lm()` but will be a foundation for futher tidymodel workflows.

```{r}
#hey train lm!!!
#advantage is there are a lot of different 'engine/model' types
lm_spec <- linear_reg() %>% 
  set_engine(engine = 'lm')

lm_fit <- lm_spec %>% fit(weekly_attendance ~ ., data = nfl_train)

```

What's nice is you can `tidy()` it.

```{r}
tidy(lm_fit) %>%  arrange(-estimate)
```

Now let's do random forest.

```{r}
rf_spec <- rand_forest(mode = 'regression') %>% 
  set_engine('ranger')

rf_fit <- rf_spec %>% fit(weekly_attendance ~ ., data = nfl_train)


```

Yeah we trained our models!

##Evaluate model

Let's compare how our training data did by using our test data.

```{r}
results_train <- lm_fit %>% predict(new_data = nfl_train) %>% 
  mutate(truth = nfl_train$weekly_attendance,
         model = 'lm') %>% 
  bind_rows(rf_fit %>% predict(new_data = nfl_train) %>% 
  mutate(truth = nfl_train$weekly_attendance,
         model = 'rf'))

results_test <- lm_fit %>% predict(new_data = nfl_test) %>% 
  mutate(truth = nfl_test$weekly_attendance,
         model = 'lm') %>% 
  bind_rows(rf_fit %>% predict(new_data = nfl_test) %>% 
  mutate(truth = nfl_test$weekly_attendance,
         model = 'rf'))
```

Now let's check the results with RMSE.

```{r}
results_train %>% 
  group_by(model) %>% 
  rmse(truth = truth, estimate = .pred)

results_test %>% 
  group_by(model) %>% 
  rmse(truth = truth, estimate = .pred)
```

As always IMO, random forest overfits... Bias/variance trade-offs.

```{r}
results_test %>% 
  mutate(train = 'testing') %>% 
  bind_rows(results_train %>% 
              mutate(train = 'training')) %>% 
  ggplot(aes(truth, .pred, color = model)) + 
  geom_abline() + geom_point(alpha = 0.2) + facet_wrap(~train)
```


# Let's try again

Now let's use resampling!

```{r}
set.seed(123)

nfl_folds <- vfold_cv(nfl_train,strata = playoffs)

rf_result <- fit_resamples(
  rf_spec,
  weekly_attendance ~ ., 
  nfl_folds,
  control = control_resamples(save_pred = TRUE)
)

rf_result %>% collect_metrics()
```

The power of resampling!


```{r}
rf_result %>% 
  unnest(.predictions) %>% 
  ggplot(aes(weekly_attendance, .pred, color = id)) + 
  geom_point(alpha = 0.4) + scale_x_continuous(labels = comma) + scale_y_continuous(labels = comma) + geom_abline()
```

































