---
title: 'Video 8: Tune RF'
author: "Josh Erickson"
date: "7/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

theme_set(theme_bw())
```

Let's tune a RF model using tidymodels for [Trees in San Francisco  from #tidytuesday data](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-01-28/readme.md)


## Explore Data

```{r}
# Get the Data

tuesdata <- tidytuesdayR::tt_load('2020-01-28')


sf_trees <- tuesdata$sf_trees

sf_trees %>% count(legal_status, sort = T)
sf_trees %>% count(legal_status, caretaker, wt = dbh, sort = T)

#try to predict legal status.
trees_df <- sf_trees %>% 
  mutate(legal_status = case_when(legal_status == "DPW Maintained" ~ legal_status,
                                  TRUE ~ "Other"),
         plot_size = parse_number(plot_size)) %>% select(-address) %>% na.omit() %>% 
  mutate(across(where(is.character), as.factor))

#for spatial autocorr
Mycluster80 <- kmeans(trees_df[,c('longitude','latitude')], (nrow(trees_df)/80)) 
trees_df$spatial_cluster80 = Mycluster80$cluster

```

```{r}
library(skimr)
skim(trees_df)
```

```{r}
library(sf)
trees_sf <- st_as_sf(trees_df, coords = c('longitude', 'latitude'))
trees_sf %>% 
  ggplot() + geom_sf(aes(color = legal_status), size = 0.25, alpha = 0.5)
```

Let's look at the caretakers
```{r}
trees_df %>% 
  count(legal_status, caretaker, sort = T) %>% 
  add_count(caretaker, wt = n, name = 'caretaker_count') %>% 
  filter(caretaker_count > 50) %>% 
  group_by(legal_status) %>% 
  mutate(percent_legal = n/sum(n)) %>% 
  ggplot(aes(percent_legal, caretaker, fill = legal_status)) +
  geom_col(position = 'dodge')
```

## build model

```{r}
library(tidymodels)
set.seed(1234)
trees_split <- initial_split(trees_df, strata = legal_status)

trees_train <- training(trees_split)
trees_test <- testing(trees_split)
```

Data pre-processing

```{r}
tree_rec <- recipe(legal_status ~., data = trees_train) %>% 
  update_role(tree_id, new_role = 'ID') %>% 
  step_other(c('species','caretaker'),threshold = 0.01) %>% 
  step_other(site_info, threshold = 0.005) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_date(date, features = c('year')) %>% 
  step_rm(date, longitude, latitude) %>% 
  themis::step_downsample(legal_status)

tree_prep <- prep(tree_rec)
tree_juiced <- juice(tree_prep)

tree_juiced %>% count(date_year, sort = TRUE)

```

Now make the model specs

```{r}
tune_spec <- rand_forest(
  mtry = tune(),
  trees = 1000,
  min_n = tune()
  ) %>% 
  set_mode('classification') %>% 
  set_engine('ranger')


```

For convienence set up a workflow.

```{r}
tune_workflow <- workflow() %>% 
  add_recipe(tree_rec) %>% 
  add_model(tune_spec)
```

## Train hyperparams

Let's do 10-fold cv; however, let's do spatial cv
```{r}

Mycluster80 <- kmeans(trees_train[,c('longitude','latitude')], (nrow(trees_train)/80)) 
trees_train$spatial_cluster80 = Mycluster80$cluster

trees_train_sf <- trees_train %>% st_as_sf(coords = c('longitude', 'latitude'))
trees_train_sf %>% 
  ggplot() + geom_sf(aes(color = spatial_cluster80), show.legend = F) +
  scale_color_distiller(palette = 'Paired')

#now we can set strata to spatial_cluster80
set.seed(234)
trees_fold <- vfold_cv(trees_train, strata = spatial_cluster80)

```

```{r}
doParallel::registerDoParallel()

set.seed(355)
tune_res <- tune_grid(
  tune_workflow,
  resamples = trees_fold,
  grid = 20
)
```

```{r}
best_auc <- tune_res %>% select_best('roc_auc')
tune_res %>% 
  collect_metrics() %>% 
  filter(.metric == 'roc_auc') %>% 
  select(mean, min_n, mtry) %>% 
  pivot_longer(min_n:mtry, 
              values_to = 'value',
              names_to = 'parameter') %>% 
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = F) +
  facet_wrap(~parameter, scales = 'free')
```

Tune again but just make a new grid.

```{r}
rf_grid <- grid_regular(
  mtry(range = c(10, 40)),
       min_n(range = c(2,10)),
       levels = 5
)

regular_res <- tune_grid(
  tune_workflow,
  resamples = trees_fold,
  grid = rf_grid
)
```

GOing to use mtry = 15 and min_n = 2

```{r}

final_rf <- finalize_model(
  tune_spec,
  best_auc
)
```

Let's look at variable importance.

```{r}
final_rf %>% 
  set_engine('ranger', importance = 'permutation') %>% 
  fit(legal_status~., data = juice(tree_prep) %>% select(-tree_id, -spatial_cluster80)) %>% 
  vip::vip(geom = 'point')
```

```{r}
final_wf <- workflow() %>% 
  add_recipe(tree_rec) %>%
  add_model(final_rf)

final_res <- final_wf %>% 
  last_fit(trees_split)

final_res %>% 
  collect_metrics()

```

