---
title: 'Video 6: Data Preprocessing and Resampling'
author: "Josh Erickson"
date: "7/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)

theme_set(theme_bw())
```

Let's train models using tidymodels for [US colleges and tuition and who attends from #tidytuesday data](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-03-10/readme.md)


## Explore Data

```{r}
# Get the Data

tuesdata <- tidytuesdayR::tt_load('2020-03-10')


tuition_cost <- tuesdata$tuition_cost

diversity_raw <- tuesdata$diversity_school
```

Now explore; look out for highly correlated variables for certain models.
```{r}
diversity_raw %>% count(category, sort = T)
```

Let's look at `Total Minority`

```{r}
diversity_school <- diversity_raw %>% 
  filter(category == 'Total Minority') %>% 
  mutate(total_minority = enrollment/total_enrollment)

diversity_school %>% 
  ggplot(aes(total_minority)) +
  geom_histogram(alpha = 0.75)
```

Let's try and understand/predict what is related to colleges with more ethnic/minority students compared to the contrary.

```{r}

university_df <- diversity_school %>% 
  transmute(diversity = case_when(total_minority > 0.3 ~ 'high',
                                  TRUE ~ 'low'),
            name, state, total_enrollment) %>% 
           inner_join(tuition_cost %>% select(name, type, degree_length,
                                              in_state_tuition:out_of_state_total)) %>% 
  left_join(tibble(state = state.name, region = state.region)) %>% 
  select(-state, -name) %>% 
  mutate(across(where(is.character), factor))

library(skimr)
skim(university_df)
```

Let's do a quick exploratory plot.

```{r}
university_df %>% 
  ggplot(aes(type, in_state_tuition, fill = diversity)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::dollar_format()) +
  facet_wrap(~region)

university_df %>% 
  ggplot(aes(type, total_enrollment, fill = diversity)) +
  geom_boxplot() + scale_y_log10(labels = scales::comma_format()) +
  facet_wrap(~region)
```

## Start building models

```{r}
library(tidymodels)

set.seed(123)
uni_split <- initial_split(university_df, strata = diversity)

uni_train <- training(uni_split)
uni_test <- testing(uni_split)

#preprocessing

uni_rec <- recipe(diversity ~ ., data = uni_train) %>% 
  step_corr(all_numeric()) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_numeric()) %>% 
  step_normalize(all_numeric()) %>% 
  prep()
# you can get data out with juice
juice(uni_rec)
```

Start modeling with logistic regression.

```{r}
glm_spec <- logistic_reg() %>% 
  set_engine('glm')

glm_fit <- glm_spec %>% 
  fit(diversity~., data = juice(uni_rec))


```

Now nearest neighbors.

```{r}
knn_spec <- nearest_neighbor() %>% 
  set_engine('kknn') %>% 
  set_mode('classification')

knn_fit <- knn_spec %>% 
  fit(diversity~., data = juice(uni_rec))

tree_spec <- rand_forest() %>% 
  set_engine('randomForest') %>% 
  set_mode('classification')

tree_fit <- tree_spec %>% 
  fit(diversity~., data = juice(uni_rec))

```

## Evaluate models with resampling

```{r}

set.seed(123)
folds <- vfold_cv(juice(uni_rec), strata = diversity)

set.seed(3322)

glm_rs <- glm_spec %>% 
  fit_resamples(diversity~., resamples = folds,
                metrics = metric_set(roc_auc, sens, spec, accuracy, kap, j_index),
                control = control_resamples(save_pred = TRUE))


knn_rs <- knn_spec %>% 
  fit_resamples(diversity~., resamples = folds,
                metrics = metric_set(roc_auc, sens, spec, accuracy, kap, j_index),
                control = control_resamples(save_pred = TRUE))

tree_rs <- tree_spec %>% 
  fit_resamples(diversity~., resamples = folds,
                metrics = metric_set(roc_auc, sens, spec, accuracy, kap, j_index),
                control = control_resamples(save_pred = TRUE))


```

Now bind the resample results together.

```{r}
glm_rs %>% 
  unnest(.predictions) %>% 
  mutate(model = 'glm') %>% 
  bind_rows(knn_rs %>% 
  unnest(.predictions) %>% 
  mutate(model = 'knn')) %>% 
  bind_rows(tree_rs %>% 
  unnest(.predictions) %>% 
  mutate(model = 'rf')) %>% 
  group_by(model) %>% 
  roc_curve(diversity, .pred_high) %>% 
  autoplot()

#or plot spec/sens
glm_rs %>% 
  unnest(.predictions) %>% 
  mutate(model = 'glm') %>% 
  bind_rows(knn_rs %>% 
  unnest(.predictions) %>% 
  mutate(model = 'knn')) %>% 
  bind_rows(tree_rs %>% 
  unnest(.predictions) %>% 
  mutate(model = 'rf')) %>% 
  group_by(model) %>% 
  roc_curve(diversity, .pred_high) %>% 
  pivot_longer(c(specificity, sensitivity), names_to = 'metric') %>% 
  ggplot(aes(.threshold, value, color = metric)) +
  geom_line() + facet_wrap(~model)
```

Let's wrap it up and look at the test data.

```{r}
tree_fit %>% 
  predict(new_data = bake(uni_rec, new_data = uni_test),
          type = 'prob') %>% 
  mutate(truth = uni_test$diversity) %>% 
  roc_auc(truth, .pred_high)


```

